Explaining Amsterdam House Prices with Greenness

### 2023-04-11 README.Rmd

---
title: "Explaining Amsterdam House Prices with Greenness"
subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression"
author: "Yúri Grings, Thomas Nibbering, Jitse Ruurd Nauta"

@@

Below a short overview of the structure of the GitHub page, methodology, data sources, and code is provided.

@@

Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb):

>>>>

---
title: "Explaining Amsterdam House Prices with Greenness"
subtitle: "An Empirical Study using Remote Sensing and Geographically Weighted Regression"

@@

Below is a short overview of the structure of the GitHub page, methodology, data sources, and code.

@@

Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:
